### 2020-06-15 Report/aws_325ghz_study.tex
added AWS-4X, and some new text

The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
calibration process. The bandwidth applied is the one found in columns 3 of
Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
15\,km resolution at 183\,GHz. This time was estimated to 3\,ms.

@@

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

\subsection{A three channel option}
%
The ICI channels give a rough RH weighting functions matching with AWS-32,
AWS-33 and AWS-34 (Fig.~\ref{fig:wf:mls:025}), and to find a tentative three
channel option an even better matching was used as constrain to set the
specifications. The resulting values are found in Table~\ref{tab:chs:prel} and
example weighting functions are displayed in Fig.~\ref {fig:3ch:prel}. This
option has a IF range of 1.0 to 8.0\,GHz, and leaves a 100\,MHz space between
AWS-42 and AWS-43, and 200\,MHz space between AWS-41 and AWS-42. That is, the
suggestion uses the complete IF bandwidth as far as possible, that is
technically possible.

\begin{table}[!t]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.55 & 2500\\
    AWS-43  & 325.15$\pm$1.60 & 1200\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800\\
    AWS-42  & 325.15$\pm$4.10 & 1800\\
    AWS-43  & 325.15$\pm$2.40 & 1200\\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
%  \begin{tabular}[c]{c|c|c}
%    Channel & Frequency   & Bandwidth \\
%    name    & [GHz] &  [MHz] \\
%    \hline
%    AWS-41  & 325.15$\pm$6.60 & 2800\\
%    AWS-42  & 325.15$\pm$4.05 & 1900\\
%    AWS-43  & 325.15$\pm$2.35 & 1300\\
%    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
%    \hline
%  \end{tabular}
  \end{minipage}  
  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
    of three (left) and four (right) channels.}
  \label{tab:chs:prel}
\end{table}

\subsection{A four channel option}
%
The tentative four channel option in Table~\ref{tab:chs:prel} gives a broader
altitude coverage, towards higher altitudes, and offers weighting functions
roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between all the
325\,GHz channels. Also this suggestion uses the complete IF bandwidth.

@@

\begin{table}[!h]
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.30 & 3000\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

@@

\subsubsection{Training}
%  
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
		\hline

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.000 & 0.888  &              0.005 &      - \\
uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\

@@

\subsection{Uncertainty estimation}
%

\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K. }
	\label{fig:prediction_uncertainty}
\end{figure}

@@

\subsection{T rec = 1800}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      0.000 \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      0.000 \\
	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 , Trec = 1800}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
	corrected (four channel)   &  0.048 & 0.606 &             -1.112 &      4.264 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
	corrected (four channel)   &  0.079 & 0.630 &             -0.399 &      2.981 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\subsection{T rec = 2400}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ AWS-32, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 2400  }
	\label{tab:qrnn:C36}
\end{table}

>>>>

The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
calibration process. The bandwidth applied is the one found in columns 3 of
Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
10\,km resolution at 183\,GHz. This time was estimated to 3\,ms.

@@

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel3}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel4}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

\subsection{A three channel option}
%
The ICI channels give a rough RH weighting functions matching with AWS-32,
AWS-33 and AWS-34 (Fig.~\ref{fig:wf:mls:025}), and to find a tentative three
channel option an even better matching was used as constrain to set the
specifications. The resulting values are found in Table~\ref{tab:chs:prel3} and
example weighting functions are displayed in Fig.~\ref {fig:3ch:prel}. This
option has a IF range of 1.0 to 8.0\,GHz, and leaves a 100\,MHz space between
AWS-42 and AWS-43, and 200\,MHz space between AWS-41 and AWS-42. That is, the
suggestion uses the complete IF bandwidth as far as possible, that is
technically possible.

\begin{table}[!t]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a three 325\,GHz channels option. The
    values in the three last columns is the 1$\sigma$ noise level according to
    Eq.~\ref{eq:noise}, for $T_a=300$\,K and  $T_r$ }
  \label{tab:chs:prel3}
\end{table}

\begin{table}[!t]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
    Table~\ref{tab:chs:prel4}.}
  \label{tab:chs:prel4}
\end{table}

\subsection{A four channel option}
%
The tentative four channel option in Table~\ref{tab:chs:prel4} gives a broader
altitude coverage, towards higher altitudes, and offers weighting functions
roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between all the
325\,GHz channels. Also this suggestion uses the complete IF bandwidth.

@@

\begin{table}[!h]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
		\hline

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline

@@

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.000 & 0.888  &              0.005 &      - \\
uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\

@@

\subsection{Uncertainty estimation}
%
Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target. The outputs from QRNN model are subject to uncertainty which can be modeled by the prediction intervals.

In our QRNN model, we estimate the conditional quantiles for  median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$. The predictions for each quantile are used to construct the confidence intervals. The confidence interval for each point estimate is a way to quantify its uncertainty. For example, the predicted quantiles for $\pm 1 \sigma$ give 68\% probability that the true value will lie between the range.

If the posterior distribution from QRNN follow normal distribution, the uncertainty can be estimated as a gaussian distribution centered around the median and standard deviation equal to the estimated error. To inspect if the predictions follow a normal distribution we evaluate the length of confidence intervals with respect to the median. Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (using four channel option). The uncertainty with respect to the median for 1000 randomly selected cases is shown. The red line represents the uncertainty in a hypothetical Gaussian distribution  of $270\pm0.62$\,K. If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on. The predictions from our QRNN model seem to be symmetric around the median for the 95\% confidence interval ($\pm 2 \sigma$). In other words, around 95\% of the true cases lie in the confidence interval given by $\pm 2\sigma$, and only 6\% of predictions are either too low or too high than the true value.

A similar uncertainty quantification for other 183\,GHz channels also gives similar results. Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution. 
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K. }
	\label{fig:prediction_uncertainty}
\end{figure}

\subsection{QRNN using AWS-4X}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{Channel_C32_C4X.png}
	\caption{ }
	\label{fig:qrnn_C32_C4X:deviations}
\end{figure}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 with AWS-4X}
	\label{tab:qrnn:C32:C4X}
\end{table} 
We also tested the QRNN model to predict cloud-free TBs using AWS-4X. In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32. The model was trained as described in Section~\ref{sec:qrnn:training}, but the width of the network was chosen to be 256 neurons. Other structural and training parameters remain unchanged.

Figure~\ref{fig:qrnn_C32_C4X:deviations} shows the error distributions for the differences between the predicted values and clear-sky simulations for AWS-32. The corresponding statistics are shown in Table~\ref{tab:qrnn:C32:C4X}. The results from QRNN model trained with four channel option of 325\,GHz are also shown for comparison.

@@

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 , Trec = 1800}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
	corrected (four channel)   &  0.048 & 0.606 &             -1.112 &      4.264 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
	corrected (four channel)   &  0.079 & 0.630 &             -0.399 &      2.981 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ AWS-32, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 2400  }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                      & -0.001 & 0.638 &              0.006 &      0.000 \\
uncorrected                 & -0.676 & 3.688 &            -10.299 &      0.000 \\
 corrected (three channela) &  0.069 & 0.655 &             -0.396 &      2.666 \\
corrected (three channelb)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}
